R Notebook

### 2022-04-22 R/HumanDeaminationAnalysis.rmd
Update HumanDeaminationAnalysis.rmd

```{r purine_vs_pyrimidine_frequencies_across_read_length, fig.width = 11, fig.height = 5}

plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1, THREE_PRIME,
                               title = "CPD Rep1 3' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2, THREE_PRIME,
                               title = "CPD Rep2 3' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1, FIVE_PRIME,
                               title = "CPD Rep1 5' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2, FIVE_PRIME,
                               title = "CPD Rep2 5' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))

plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, THREE_PRIME,
                               title = "6-4 Rep1 3' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, THREE_PRIME,
                               title = "6-4 Rep2 3' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, FIVE_PRIME,
                               title = "6-4 Rep1 5' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, FIVE_PRIME,
                               title = "6-4 Rep2 5' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))

@@

plotNucFreqVsReadLengthBarPlot(rbindlist(lapply(CPDSingleCToTMismatchData$rep1,
                               THREE_PRIME, title = "CPD Rep1 3' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2,
                               THREE_PRIME, title = "CPD Rep2 3' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1,
                               FIVE_PRIME, title = "CPD Rep1 5' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2,
                               FIVE_PRIME, title = "CPD Rep2 5' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))

plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, THREE_PRIME,
                               title = "6-4 Rep1 3' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, THREE_PRIME,
                               title = "6-4 Rep2 3' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, FIVE_PRIME,
                               title = "6-4 Rep1 5' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, FIVE_PRIME,
                               title = "6-4 Rep2 5' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))

>>>>

```{r purine_vs_pyrimidine_frequencies_across_read_length, fig.width = 11, fig.height = 5}
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1, THREE_PRIME,
                               title = "CPD Rep1 3' Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2, THREE_PRIME,
                               title = "CPD Rep2 3' Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1, FIVE_PRIME,
                               title = "CPD Rep1 5' Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2, FIVE_PRIME,
                               title = "CPD Rep2 5' Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))

plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, THREE_PRIME,
                               title = "6-4 Rep1 3' Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, THREE_PRIME,
                               title = "6-4 Rep2 3' Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, FIVE_PRIME,
                               title = "6-4 Rep1 5' Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, FIVE_PRIME,
                               title = "6-4 Rep2 5' Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
```

```{r filter_by_mismatch_pos_and_read_length}
CPDFilteredSingleCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) {
  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
})
sixFourFilteredSingleCToTMismatchData = lapply(sixFourSingleCToTMismatchData, function(x) {
  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
})
```

@@

plotNucFreqVsReadLengthBarPlot(lapply(CPDFilteredSingleCToTMismatchData$rep1, getFirstPositionQuartile),
                               THREE_PRIME, title = "CPD Rep1 1st Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(lapply(CPDFilteredSingleCToTMismatchData$rep2, getFirstPositionQuartile),
                               THREE_PRIME, title = "CPD Rep2 1st Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))

plotNucFreqVsReadLengthBarPlot(lapply(sixFourFilteredSingleCToTMismatchData$rep1, getFirstPositionQuartile),
                               THREE_PRIME, title = "6-4 Rep1 1st Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(lapply(sixFourFilteredSingleCToTMismatchData$rep2, getFirstPositionQuartile),
                               THREE_PRIME, title = "6-4 Rep2 1st Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
```

```{r purine_vs_pyrimidine_frequencies_last_quartile_mismatch_pos, fig.width = 11, fig.height = 5}

plotNucFreqVsReadLengthBarPlot(lapply(CPDFilteredSingleCToTMismatchData$rep1, getLastPositionQuartile),
                               THREE_PRIME, title = "CPD Rep1 4th Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(lapply(CPDFilteredSingleCToTMismatchData$rep2, getLastPositionQuartile),
                               THREE_PRIME, title = "CPD Rep2 4th Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))

plotNucFreqVsReadLengthBarPlot(lapply(sixFourFilteredSingleCToTMismatchData$rep1, getLastPositionQuartile),
                               THREE_PRIME, title = "6-4 Rep1 4th Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(lapply(sixFourFilteredSingleCToTMismatchData$rep2, getLastPositionQuartile),
                               THREE_PRIME, title = "6-4 Rep2 4th Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
```
